% Resume source file for download from the portfolio.
% Compile this in Overleaf or with pdfLaTeX.

\documentclass[a4paper,10pt]{article}
\usepackage[left=0.5in, right=0.5in, top=0.42in, bottom=0.42in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage[T1]{fontenc}
\usepackage{microtype}

\definecolor{linkblue}{HTML}{1A56DB}
\definecolor{dark}{HTML}{111111}
\definecolor{mid}{HTML}{444444}

\hypersetup{colorlinks=true, urlcolor=linkblue, linkcolor=linkblue}

\titleformat{\section}
  {\small\bfseries\color{dark}\uppercase}
  {}{0em}{}
  [\vspace{0.5pt}\color{dark}\titlerule\vspace{1pt}]
\titlespacing{\section}{0pt}{12pt}{5pt}

\setlist[itemize]{leftmargin=1.35em,itemsep=3.5pt,topsep=3pt,parsep=0pt,label=\textbullet}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

\begin{document}
\pagestyle{empty}

\begin{center}
  {\LARGE\bfseries\color{dark} ANKIT BANSAL}\\[3pt]
  {\small\textit{\color{mid} Computer Science Engineering \ $|$ \ Full-Stack \& iOS Developer}}\\[4pt]
  {\small
    +91-8968877852 \ $|$ \
    \href{mailto:bansalankit1575@gmail.com}{bansalankit1575@gmail.com} \ $|$ \
    \href{https://www.linkedin.com/in/ankit-bansal-50828a199/}{linkedin.com/in/ankit-bansal} \ $|$ \
    \href{https://github.com/Anki-0015}{github.com/Anki-0015}
  }
\end{center}

\section*{Education}
\textbf{Chitkara University, Punjab}\hfill{\small\textit{\color{mid}Aug 2023 -- Jul 2027}}\\
{\small\color{mid}Bachelor of Engineering in Computer Science}\hfill{\small\color{mid}CGPA: 7.8}

\section*{Experience}
\textbf{iOS Application Development Intern} \textnormal{---} Infosys\hfill{\small\textit{\color{mid}Dec 2025 -- Jan 2026}}
\begin{itemize}
  \item Built SwiftUI MVVM apps for multi-role workflows with reusable component libraries.
  \item Integrated Stripe payments with tokenization and robust error handling.
  \item Led Agile ceremonies as Scrum Master for a 10-member team.
  \item Refactored architecture to decouple business logic from UI.
\end{itemize}

\section*{Technical Skills}
\textbf{Languages:} Java, JavaScript\\
\textbf{Frontend / Mobile:} React.js, SwiftUI\\
\textbf{Backend:} Node.js, Express.js, Spring Boot, REST APIs, JWT, BCrypt\\
\textbf{Databases:} MySQL, MongoDB\\
\textbf{Tools:} Git, GitHub, Postman, Linux CLI\\
\textbf{Core CS:} Data Structures \& Algorithms, OOP, DBMS, Operating Systems

\section*{Projects}
\textbf{Banking Management System}\\
\href{https://github.com/Anki-0015/bankingManagementSysteme}{github.com/Anki-0015/bankingManagementSysteme}
\begin{itemize}
  \item Full-stack banking system with JWT authentication and role-based access.
\end{itemize}

\textbf{Job Portal}\\
\href{https://github.com/Anki-0015/JobPortal}{github.com/Anki-0015/JobPortal}
\begin{itemize}
  \item REST backend with role-based routes and performance optimization.
\end{itemize}

\textbf{Concert Management System}\\
\href{https://github.com/Anki-0015/Concert-Management}{github.com/Anki-0015/Concert-Management}
\begin{itemize}
  \item Java CLI app using BST, Stack, Queue, and HashMap.
\end{itemize}

\textbf{BrewDev}\\
\href{https://github.com/Anki-0015/brewdev}{github.com/Anki-0015/brewdev}
\begin{itemize}
  \item Bash tool automating developer environment setup.
\end{itemize}

\section*{Certifications and Achievements}
\begin{itemize}
  \item Solved 250+ DSA problems on LeetCode, GeeksforGeeks, and HackerRank.
  \item Nutanix Hybrid Cloud Fundamentals (NHCF) certified.
\end{itemize}

\end{document}
